Output Summary

### 2023-05-04 03-post-process/output-plots-children/09-equiv-rates.Rmd
Update file names on output-plots children
Consistency updates: 09-equiv-rates.Rmd

```{r adults-per-smolt, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  # which years had zero hatchery smolt released
  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0

@@

  # plot natural origin time series
  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, 10))

  # add hatchery origin time series
  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(Ra_per_Ma_hor["2.5%",], rev(Ra_per_Ma_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
  lines(Ra_per_Ma_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
  lines(Ra_per_Ma_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
  lines(Ra_per_Ma_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)

  if (j == 1) {
    legend("topright", legend = origins, title = "Origin",
         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
  }
}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Adults per 100 Smolt")
```

@@

```{r bon-to-bon, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  # which years had zero hatchery smolt released
  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0

@@

  # plot natural origin time series
  plot_tseries(est = phi_nor, yrs = all_yrs[sar_yrs], main = pops[j], ylim = c(0, ymax))

  # add hatchery origin time series
  polygon(x = c(all_yrs[sar_yrs], rev(all_yrs[sar_yrs])), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
  lines(phi_hor["2.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
  lines(phi_hor["97.5%",] ~ all_yrs[sar_yrs], col = "blue", lty = 2)
  lines(phi_hor["mean",] ~ all_yrs[sar_yrs], col = "blue", lwd = 2)

  if (j == 1) {
    legend("topright", legend = origins, title = "Origin",
         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
  }
}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "BON -> BON Survival")
```

@@

```{r parr-per-spawner, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
```

@@

```{r smolt-per-spawner, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("Mb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Smolt per Spawner")
```

@@

```{r spawners-per-spawner, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("Sa_tot_per_Sa_tot[year,pop]", pop = j, year = sar_yrs)), yrs = all_yrs[sar_yrs], main = pops[j])
 abline(h = 1, lty = 2)
}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Spawner per Spawner")
```

>>>>

```{r adults-per-smolt, fig.width = p4_width, fig.height = p4_height}
j = 1

plot_fn = function(j) {
  # which years had zero hatchery smolt released
  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0

@@

  # plot natural origin time series
  plot_tseries(est = Ra_per_Ma_nor, yrs = all_yrs[sar_yrs], label_text = pops[j], ylim = c(0, 10))

  # add hatchery origin time series
  add_tseries(est = Ra_per_Ma_hor, yrs = all_yrs[sar_yrs])

  if (j == 2) {
    legend("topright", legend = origins, title = "Origin",
           pch = 22, col = main_cols[c("model", "model2")], pt.cex = 2, pt.bg = tran_cols[c("model", "model2")], bty = "n", cex = 0.8)
  }
}
mypar()
junk = sapply(1:jags_data$nj, plot_fn)
axis_labels("Brood Year", "Adults per 100 Smolt")
```

@@

```{r bon-to-bon, fig.width = p4_width, fig.height = p4_height}
plot_fn = function(j) {
  # which years had zero hatchery smolt released
  zero_hor_smolt = post_summ(post, sub_index("Mb[year,LH_type,origin,pop]", year = sar_yrs, LH_type = i_spring, origin = o_hor, pop = j))["mean",] == 0

@@

  # plot natural origin time series
  plot_tseries(est = phi_nor, yrs = all_yrs[sar_yrs], label_text = pops[j], ylim = c(0, ymax))

  # add hatchery origin time series
  add_tseries(est = phi_hor, yrs = all_yrs[sar_yrs])

  if (j == 2) {
    legend("topright", legend = origins, title = "Origin",
           pch = 22, col = main_cols[c("model", "model2")], pt.cex = 2, pt.bg = tran_cols[c("model", "model2")], bty = "n", cex = 0.8)
  }
}
mypar()
junk = sapply(1:jags_data$nj, plot_fn)
axis_labels("Brood Year", "BON \u2192 BON Survival")
```

@@

```{r parr-per-spawner, fig.width = p4_width, fig.height = p4_height}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], label_text = pops[j])
}

mypar()
junk = sapply(1:jags_data$nj, plot_fn)
axis_labels("Brood Year", "Parr per Spawner")
```

@@

```{r smolt-per-spawner, fig.width = p4_width, fig.height = p4_height}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("Mb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs)), yrs = all_yrs[ts_yrs], label_text = pops[j])
}

mypar()
junk = sapply(1:jags_data$nj, plot_fn)
axis_labels("Brood Year", "Smolt per Spawner")
```

@@

```{r spawners-per-spawner, fig.width = p4_width, fig.height = p4_height}
plot_fn = function(j) {
  plot_tseries(est = post_summ(post, sub_index("Sa_tot_per_Sa_tot[year,pop]", pop = j, year = sar_yrs)), yrs = all_yrs[sar_yrs], label_text = pops[j])
  abline(h = 1, lty = 2)
}
mypar()
junk = sapply(1:jags_data$nj, plot_fn)
axis_labels("Brood Year", "Spawners per Spawner")
```
